---
title: "Assignment 5"
author: "Jack ST"
format: html
editor: visual
---

---
title: "ASSIGNMENT 5 - TV Series: *Merlin*"
format: html
execute: 
  echo: true
  warning: false
  message: false
---

## Introduction

*Merlin* is a British fantasy-adventure drama that aired on BBC One from 20 September 2008 to 24 December 2012. The series reimagines Arthurian legends, following the young warlock Merlin as he protects Prince Arthur in a kingdom where magic is outlawed. Other notable characters include Morgana, Guinevere, and Uther Pendragon.

## Image

![Merlin Cast](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.imdb.com%2Ftitle%2Ftt1199099%2F&psig=AOvVaw3cvVAIJD0xbHk5cs1xWpW2&ust=1744121980796000&source=images&cd=vfe&opi=89978449&ved=0CBQQjRxqFwoTCOCD9euOxowDFQAAAAAdAAAAABAE)

*Main cast of **Merlin***.

## Viewership Statistics

Here is a summary of average UK viewership per season:

| Season | Episodes | First Aired | Last Aired  | Average UK Viewers (millions) |
|--------|----------|-------------|-------------|-------------------------------|
| 1      | 13       | 20 Sep 2008 | 13 Dec 2008 | 6.32                          |
| 2      | 13       | 19 Sep 2009 | 19 Dec 2009 | 5.99                          |
| 3      | 13       | 11 Sep 2010 | 4 Dec 2010  | 6.78                          |
| 4      | 13       | 1 Oct 2011  | 24 Dec 2011 | 7.17                          |
| 5      | 13       | 6 Oct 2012  | 24 Dec 2012 | 7.13                          |

*Data Source: [Wikipedia](https://en.wikipedia.org/wiki/List_of_Merlin_episodes)*

```{r}
#| label: viewership-over-time
#| fig-cap: "Average UK Viewership by Season"

library(ggplot2)

data <- data.frame(
  Season = 1:5,
  Viewers = c(6.32, 5.99, 6.78, 7.17, 7.13)
)

ggplot(data, aes(x = Season, y = Viewers)) +
  geom_line() +
  geom_point() +
  labs(x = "Season", y = "Average Viewers (millions)")
```

```{r}
#| label: viewership-change
#| fig-cap: "Change in Viewership Between Seasons"

change <- diff(c(6.32, 5.99, 6.78, 7.17, 7.13))
data_change <- data.frame(
  Season = paste0("S", 2:5),
  Change = change
)

ggplot(data_change, aes(x = Season, y = Change)) +
  geom_col() +
  labs(x = "Season", y = "Change in Viewers (millions)")
```
