---
title: "Assignment 7"
author: "Michał Budasz"
date: "07/04/2025"
format: html
editor: visual
execute:
  echo: fenced
---

```{r}
#| label = "setup",
#| include = FALSE
library(chron)
library(reticulate)
library(readr)
library(dplyr)
```

------------------------------------------------------------------------

# Information on chosen TV Series

For this assignment, I choose a well-known post-apocalyptic TV series called [The Walking Dead](https://en.wikipedia.org/wiki/The_Walking_Dead_(TV_series))

Basing on provided source, the author will provide a short report for one who wasn't lucky enough to watch it :D

------------------------------------------------------------------------

## Brief description of the show

**The Walking Dead** is an American *post-apocalyptic horror drama* television series developed by Frank Darabont, based on the comic book series of the same name by Robert Kirkman, Tony Moore, and Charlie Adlard. Together, the show and the comic book series form the core of *The Walking Dead* franchise. The series features a large ensemble cast as survivors of a *zombie apocalypse* trying to stay alive under near-constant threat of attacks from zombies known as "walkers". With the collapse of modern civilization, these survivors must confront other human survivors who have formed groups and communities with their own sets of laws and morals, sometimes leading to open conflict between them. The series is the first television series within *The Walking Dead franchise*.

## A photo with the logo of TWD series

|                                                                                                                                                                                                            |
|------------------------------------------------------------------------|
| [![Official The Walking Dead Logo.svg](//upload.wikimedia.org/wikipedia/commons/e/ef/The_Walking_Dead_2010_logo.svg){alt="Official The Walking Dead Logo.svg"}](/wiki/File:The_Walking_Dead_2010_logo.svg) |

## A summary of some basic statistics

We will base our data on [Kaggle](https://www.kaggle.com/datasets/bcruise/the-walking-dead-episodes/data) dataset (seasons 1-11)

```{r}
#| include = FALSE
twd <- read.csv("../Data/the_walking_dead_episodes.csv", header = TRUE, sep = ",")
```

### Exemplary first values for dataset

```{r}
knitr::kable(head(twd), caption = "A kable table for provided dataset")
```

### Statistical variables for number of viewers for each episode, on air date

```{r}
#| echo = TRUE
summary(twd$us_viewers)
```

## A graph of viewerships over time

```{r}
#| echo = TRUE
library(ggplot2)

twd$original_air_date <- as.Date(twd$original_air_date)

ggplot(twd, aes(x = original_air_date, y = us_viewers)) +
  geom_line(color = "darkred") +
  labs(title = "Numbers of viewers in time",
       x = "Original air date",
       y = "Number of U.S. viewers") +
  theme_minimal()
```

## A graph of season-to-season changes in viewership

### A graph of viewerships with division on seasons

```{r}
#| echo = TRUE
ggplot(twd, aes(x = original_air_date, y = us_viewers, color = factor(season))) +
  geom_line() +
  geom_point() +
  labs(
    x = "Original air date",
    y = "Number of U.S. viewers (mln)",
    color = "Season"
  ) +
  theme_minimal() +
  theme(legend.position = "right")
```

### A graph presenting difference of U.S. viewers between seasons

```{r}
#| echo = TRUE
library(dplyr)
twd$season <- as.factor(twd$season)

season_mean <- twd %>%
  group_by(season) %>% 
  summarise(viewers_mean = mean(us_viewers, na.rm = TRUE))

ggplot() +
  geom_col(data = season_mean, aes(x = season, y = viewers_mean), fill = "darkgreen", alpha = 0.7) +
  geom_jitter(data = twd, aes(x = season, y = us_viewers), color = "red", width = 0.2, alpha = 0.6, size = 2) +
  labs(
    title = "Average number of viewers in each season",
    x = "Season",
    y = "Average U.S. viewers (mln)"
  ) +
  theme_minimal()
```

## Short description of the observed changes
