---
title: "Game of Thrones Summary - Season `r params$season`"
format: pdf
params:
  season: 1
---

```{r setup, include=FALSE}
# Set chunk options
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

<!-- Introduce the report and insert the correct season -->
This report provides a summary of **Season `r params$season`** of *Game of Thrones*, based on episode-level data including titles, air dates, and viewership.

```{r load-data}
# Load the correct dataset based on the input parameter
file_path <- sprintf("Data/season_%d.csv", params$season)
got_data <- read.csv(file_path)

# Filter to ensure we’re using only the specified season
got_data <- subset(got_data, no_season == params$season)

# Preview the first few rows
head(got_data)
```

## Season `r params$season` Overview

```{r summary-stats}
# Number of episodes
num_episodes <- nrow(got_data)

# Average viewers (in millions)
avg_viewers <- round(mean(got_data$viewers, na.rm = TRUE), 2)

# Most viewed episode
most_viewed <- got_data[which.max(got_data$viewers), "title"]

# Print summary
cat(paste0("Season ", params$season, " had ", num_episodes, " episodes. ",
           "On average, each episode was watched by ", avg_viewers, " million viewers. ",
           "The most viewed episode was '", most_viewed, "'."))
```

## Viewership by Episode

```{r plot-viewers}
library(ggplot2)

ggplot(got_data, aes(x = no_season, y = viewers)) +
  geom_col(fill = "darkgreen") +
  labs(title = paste("Viewership - Season", params$season),
       x = "Episode (in season)",
       y = "Viewers (Millions)") +
  theme_minimal()
```

## Episode Table

```{r episode-table}
# Show a simple episode summary table
library(dplyr)

got_data %>%
  select(no_season, title, premiere_date, viewers) %>%
  rename(`Episode` = no_season,
         `Title` = title,
         `Air Date` = premiere_date,
         `Viewers (M)` = viewers)
```

## Conclusion

<!-- Wrap up the summary -->
Season `r params$season` of *Game of Thrones* attracted an average of `r avg_viewers` million viewers per episode. The data gives us insight into the popularity of individual episodes and how the season was received.

