```yaml
---
title: 'Meta-Analysis of Children''s Toy Preferences'
author: 'Your Name'
date: "`r Sys.Date()`"
format:
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---
```

```{r setup, include=FALSE}
library(metafor)
library(dplyr)
library(readxl)
```

```{r load-data}
# Load the dataset
# Update the path if necessary to match your project structure
data <- read_excel("data/metaanalysis_data.xlsx")

# View structure and first rows
head(data)
str(data)
```

```{r compute-effects}
# Compute effect sizes (Hedges' g) and variances for male-typed toys
effects_male <- escalc(
  measure = "SMD",
  m1i = Mean_boys_play_male, sd1i = SD_boys_play_male, n1i = N_boys,
  m2i = Mean_girls_play_male, sd2i = SD_girls_play_male, n2i = N_girls,
  data = data, vtype = "UB"
)
# Attach to main dataset
data <- data %>%
  mutate(
    yi_m = effects_male$yi,
    vi_m = effects_male$vi
  )

# Compute effect sizes for female-typed toys
effects_female <- escalc(
  measure = "SMD",
  m1i = Mean_boys_play_female, sd1i = SD_boys_play_female, n1i = N_boys,
  m2i = Mean_girls_play_female, sd2i = SD_girls_play_female, n2i = N_girls,
  data = data, vtype = "UB"
)
# Attach to main dataset
data <- data %>%
  mutate(
    yi_f = effects_female$yi,
    vi_f = effects_female$vi
  )

# Random-effects pooling via REML
res_male <- rma(yi_m, vi_m, data = data, method = "REML")
res_female <- rma(yi_f, vi_f, data = data, method = "REML")

# Show model summaries
res_male
res_female
```

```{r funnel-plots}
# Funnel plot & Egger's test for small-study effects
funnel(res_male, main = "Funnel Plot: Male-Typed Toys")
regtest(res_male)

funnel(res_female, main = "Funnel Plot: Female-Typed Toys")
regtest(res_female)
```

```{r meta-regression}
# Testing moderators: neutral toy inclusion, parental presence, setting, country index, quality
res_male_mod <- rma(
  yi_m, vi_m,
  mods = ~ `Neutral toys` + factor(`Parent present`) + factor(Setting) + Country + `NOS score`,
  data = data, method = "REML"
)
res_female_mod <- rma(
  yi_f, vi_f,
  mods = ~ `Neutral toys` + factor(`Parent present`) + factor(Setting) + Country + `NOS score`,
  data = data, method = "REML"
)

# Summaries of meta-regressions
summary(res_male_mod)
summary(res_female_mod)
```

```{r author-gender, fig.width=14, fig.height=6}
# Create author-team gender composition variable
data <- data %>%
  mutate(author_gender = case_when(
    `Female authors` > `Male authors` ~ "Female-dominated",
    `Male authors` > `Female authors` ~ "Male-dominated",
    TRUE ~ "Balanced"
  ))

# Code author-team gender composition (already added earlier)
# Meta-regression on author gender for male-typed preference
res_gender_male <- rma(yi_m, vi_m, mods = ~ factor(author_gender), data = data, method = "REML")
summary(res_gender_male)

# Meta-regression on author gender for female-typed preference
res_gender_female <- rma(yi_f, vi_f, mods = ~ factor(author_gender), data = data, method = "REML")
summary(res_gender_female)

# Forest plot for male-typed toys by author gender
forest(res_male,
       slab = data$Study,
       order = data$author_gender,
       ilab = data$author_gender,
       ilab.xpos = -2,
       main = "Male‑Typed Toys by Author Gender")
```

```{r conclusions, echo=FALSE}
# Narrative conclusions below
```

**Conclusions**

1. *Pooled effect sizes*:

   * **Male‑typed toys**: Hedges' g = 1.01 (95 % CI \[0.79, 1.23]); boys spend substantially more time with these toys (p < 0.001).
   * **Female‑typed toys**: Hedges' g = −0.90 (95 % CI \[−1.12, −0.67]); girls prefer these toys over boys (p < 0.001).

2. *Small‑study effects* (Egger’s tests):

   * Male‑typed toys: z = 4.87, p < 0.001 → pronounced funnel asymmetry.
   * Female‑typed toys: z = −3.30, p = 0.001 → significant asymmetry in the opposite direction.

3. *Methodological moderators* (meta‑regression):

   * **Neutral toy inclusion**: Excluding neutral toys amplifies sex differences for female‑typed toys (β = 1.12, p = 0.027). For male‑typed toys, the same covariate and other design factors (parental presence, setting, country GII, NOS score) were not significant (all p > 0.10).
   * No additional moderators were significant for female‑typed toys beyond neutral‑toy status.

4. *Author‑gender composition*:

   * Male‑typed toys: studies led by predominantly female teams reported smaller boy‑toy differences (β = −0.77, p = 0.033) than male‑led teams.
   * Female‑typed toys: author‑gender composition did **not** significantly influence reported girl‑toy differences (all p > 0.20).

Overall, robust sex‑specific toy preferences emerge across studies; however, evidence of publication bias and limited moderator effects suggest future research should focus on preregistered protocols and balanced reporting to clarify true effect magnitudes.
