---
title: "Assignment Quanto 3"
author: Michał Budasz
date: today
output: html_document
params:
  season: 1
  description: "some_text"
---
```{r}

# Let's load the data for each season
load(paste0("../Data/season_",params$season,".RData"))

```

# Game of Thrones - Season 'r params$season' summary in numbers

### __(*Warning:* spoilers ahead)__

***

### Overview

(From the [Wikipedia](https://en.wikipedia.org/wiki/Game_of_Thrones#Premise)) Game of Thrones is an American fantasy drama television series created by David Benioff and D. B. Weiss for HBO. It is an adaptation of A Song of Ice and Fire, a series of fantasy novels by George R. R. Martin, the first of which is A Game of Thrones.

'r params$description' 


***

### Season 'r params$season' summary

```{r}
echo=FALSE

library(stringr)
episodes_no<-nrow(season_data)

show_start<-str_sub(season_data$premiere_date,-11,-2)[1]
show_end<-str_sub(season_data$premiere_date,-11,-2)[episodes_no]

avg_viewers<- mean(season_data$viewers)

viewers_start<-season_data$viewers[1]
viewers_end<-season_data$viewers[episodes_no]

if (viewers_start<viewers_end){
  change <- "growing"
} else {
  change <- "declining"
}

most_popular_title <- season_data$title[which.max(season_data$viewers)]
most_popular_description <- season_data$description[which.max(season_data$viewers)]
```

Season 'r params$season' of Game of Thrones consisted of 'r episodes_no' episodes that aired between 'r show_start' and 'r show_end' on HBO. The show gathered an average of 'r avg_viewers' first-day TV viewers in the US, with the number 'r change' from 'r viewers_start'  to 'r viewers_end' million by the end of the season.

The most popular episode of the season was 'r most_popular_title', in which:

> 'r most_popular_description'

***

You can see how the viewership of the episodes changed in Figure 1.

```{r}
#| label = "viewers_plot"
plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

***

Finally, the episodes with the above-average viewership were:

| No. in season | Title  | Directed by  |
|:------        |:-----: |:------:      |
| 5             | "The Wolf and the Lion"  | Brian Kirk      |
| 8             | "The Pointy End" | Daniel Minahan      |
| 9             | "Baelor" | Alan Taylor      |
| 10            | "Fire and Blood" | Alan Taylor      |
